---
title: "Web Data Collection Assignment: R primer I"
author: "Simon Munzert"
output: html_document
---


```{r setup, include=FALSE}
source("../packages.r")
```


<br>

##### 1. NYC flights

Use the "nycflights13" package to answer the following questions!

a. How many variables and observations does the data.frame "flights" from the nycflights13 package contain?
b. Select the flights that started from NYC at the first day of each month!
c. Sort flights by time of arrival!
d. How many flights started from all the NYC airports in 2013?
e. Which carrier had the biggest mean net delay (departure delay minus arrival delay), which the lowest?
f. Inspect visually how the net delays are distributed!

```{r}
library(nycflights13)
nrow(flights)
```

<span style="color:blue">
Add comment like this! (just copy the <span>...</span> lines for future comments in the Rmd file.)
</span>


<br>

##### 2. Baby names

Use the "babynames" package to answer the following questions!

a. Which time period does the data frame cover?
b. What has been the most frequent name in the US since 1880? (hint: you might need the group_by() as well as the sum() function)
c. Use graphical means to determine since which year the name "Kim" became more popular as a female than a male name! (hint: grouping by two variables is helpful here! For the plot, use "year" on the x axis and "total count" on the y axis! Furthermore, this Stackoverflow post helps you understand how to plot two lines in one chart: https://stackoverflow.com/questions/2564258/plot-two-graphs-in-same-plot-in-r)

```{r}
# add code here!
```


