---
title: "Web Data Collection Assignment: Regular expressions"
author: "Simon Munzert"
output: html_document
---


### 0. Preparation: Load packages

```{r load packages}
library(stringr)
```



### 1. The ultimate regular expression

Find a regular expression that matches any text!


```{r}
# your code here
```


### 2. Finding strings that are matched by regular expressions

Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

a. [0-9]+\\$
b. b[a-z]{1,4}
c. .*?\\.txt$
d. \\d{2}/\\d{2}/\\d{4}
e. <(.+?)>.+?</\\1>

```{r}
# Example
str_extract_all("Phone 150$, TV 690$", "[0-9]+\\$") # Answer: describes prices in dollars
# your code here
```


### 3. Manipulating an email address

Consider the mail address  datalover89[at]aol[dot]com. Now, complete the following tasks.

a. Transform the string to a standard mail format (i.e., replace the square brackets with the appropriate symbols) using regular expressions.
b. Now extract the local-part ("datalover89") and the domain ("aol") separately. 

```{r}
email <- "datalover89[at]aol[dot]com"
# your code here
```


### 4. A secret message
The following code hides a secret message. Crack it with R and regular expressions. Once you have cracked it, try to collapse the solution in one single string. <i>Hint: Some of the characters are more revealing than others!</i>

```{r}
secret <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.RqoE65fGEa1otfb7wXm24k.6t3sH9zqe5fy89n6Ed5t9kc4fR905gmc4Ogxo5nhk!gr"
```



### 5. Inspecting Trump's tweets

The following code gives you access to a dataset of Donald Trump tweets that he posted over the course of the 2016 election campaign. Focus on the `Tweet_Text` variable and come up with your own shot at this data. Requirement: Use at least 3 different regular expressions and 3 different functions from the `stringr` package for your analysis!

```{r, warning = FALSE, message = FALSE}
library(readr)
trump_df <- read_csv("https://raw.githubusercontent.com/Currie32/Tweet-Like-Trump/master/tweets.csv")
```