---
title: "Web Scraping: Assignment 5"
author: "Simon Munzert"
output: html_document
---


### 0. Preparation: Load packages

```{r load packages}
# enter code here
```


### 1. Downloading HTML files from Wikipedia

Continuing with the task from the last assignment (getting data from https://en.wikipedia.org/wiki/List_of_tallest_buildings), the goal is now to download the Wikipedia pages behind the links that lead to the articles on the buildings under construction. To that end, 

a. create a set of links referring to these buildings from the first column of the table,
b. create a folder "skyscraper_htmls", and
c. download the HTML files to that folder.

In completing these tasks, implement a server-friendly scraping workflow. Finally, check the number of files in that folder. 


```{r}
# enter code here
```


### 2. Creating a map of world capitals

Take a look at https://en.wikipedia.org/wiki/List_of_national_capitals_in_alphabetical_order and complete the following tasks:

a. Extract the geographic coordinates of each European country capital (no API use; stay on the Wikipedia platform to gather the needed information). 
b. Using these coordinates, visualize the capitals on a map using the `maps` package.

```{r}
# enter code here
```



### 3. Querying the Academy Awards Acceptance Speech Database

Go to http://aaspeechesdb.oscars.org/ and use R to search the database for occurrences of "woman" or "women" in speeches by male actors in a supporting or leading role. Parse the output (year of the speech given plus actor/movie) into one data frame and print it out!
 
```{r}
# enter code here
```






